### 2018-03-08 Project log/multiple_outcomes_project_log.Rmd
,

>>>>

<!-- NEW SECTION -->
\section{Notes on Ying's MIDUS paper}

\subsection{Variables}
\begin{itemize}
\item Parental warmth ($X$): average of separate maternal and paternal warmth scales (so $\in [1,4]$)
\item {Flourishing (main $Y$)
  \begin{itemize}
  \item Continuous version: Sum of standardized subscales for emotional, psychological, and social well-being
  \item Binary version: Are you in top tertile on enough subscales?
  \item Count version: For how many subscales are you in top tertile? ($\in [0,13]$?)
  \end{itemize}
}
\item Subdomains comprising flourishing: 13 continuous measures (T3)
\item Bad outcomes (secondary $Y$s): 7 mental health problems and bad behaviors, all binary (T4)
\end{itemize}

\subsection{Analyses}
\begin{itemize}
\item Continuous flourishing and other continuous $Y$s: Normal GEE (cluster by siblings)
\item Binary flourishing: Poisson GEE with log link (risk ratios) (\hl{Did log-binomial not converge or other reason for choosing this?})
\item Count flourishing: Normal GEE (\hl{Why not, e.g., Poisson or NB?})
\item Bad binary outcomes: Poisson GEE for non-rare (RRs) or logistic regression for common (ORs)
\end{itemize}

\subsection{Our analyses}
\begin{itemize}
\item Multiple imputation for main analyses?
\item Randomly choose 1 sibling from each sibship to avoid clustering? Then just use OLS and regular log-linear model. Or could do mixed model, but then parametric bootstrap is more complicated.
\item Maybe treat outcomes as: 3 different flourishing variables + 7 binary bad outcomes? Also addresses model specification angle. 
\item 
\end{itemize}
